Simulating cosmic variance in Weak Lensing: effects on parameter inferences

### 2015-11-23 Paper/paper.tex
updated figure 5

\begin{figure*}
\includegraphics[scale=0.3]{Figures/effective_nb.eps}
\includegraphics[scale=0.3]{Figures/effective_nb_fake_uncorrected.eps}
\includegraphics[scale=0.3]{Figures/effective_nb_fake_corrected.eps}
\caption{Effective dimesionality of the feature space, $D$, as a function of the number of bands $N_b$, for the features outlined in Table \ref{featuretable}. The solid black lines show the theory predictions from equations (\ref{dodelsonscaling}) in the left panel, equation (\ref{mockscalinguncorrected}) in the right panel and equation (\ref{mockscalingcorrected}) in the bottom panel.}
\label{effectivenb}
\end{figure*}

@@

\begin{equation}
\h{\Sigma}_\bb{p} = \bb{F}^{-1} + \bb{F}^{-1}\left(- \delta{\bbh{F}}+ \delta{\bbh{F}}\bb{F}^{-1}\delta{\bbh{F}}\right)\bb{F}^{-1}  
\end{equation}  
%
If we use the precision estimator $\bbh{\Psi}=\bb{\Psi}+\delta\bbh{\Psi}$ and do not correct for the bias (\ref{psibias}), we have to use the facts that
\begin{equation}
\begin{matrix}
& \langle\delta\bbh{\Psi}\rangle = \frac{1+N_b}{N_r-N_b-2}\bb{\Psi} \\ \\
& \langle\delta\h{\Psi}_{ij}\delta\h{\Psi}_{kl}\rangle = \frac{A([N_r-1)^2+(1+N_b)^2]\Psi_{ij}\Psi_{kl} + B(N_r-1)^2(\Psi_{ik}\Psi_{kl}+\Psi_{il}\Psi_{jk})}{(N_r-N_b-2)^2}
\end{matrix}
\end{equation}
%
Keeping only the leading order $O(1/N_r)$ in the expansion we get the results
\begin{equation}
\label{explanationuncorrected}
\begin{matrix}
& \langle\delta\bbh{F}\rangle = \left(\frac{1+N_b}{N_r}\right)\bb{F} \\ \\
& \langle\delta{\bbh{F}}\bb{F}^{-1}\delta{\bbh{F}}\rangle = B(1+N_p)\bb{F}
\end{matrix}
\end{equation}
%
which leads immediately to (\ref{mockscalinguncorrected}). Now suppose we correct for the bias in the precision estimator, and use the unbiased $\bbh{\Psi}$ for which $\delta\bbh{\Psi}=0$. This leads to equation (\ref{psifluctuations}) for the quadratic fluctuations in the precision matrix, and to the same (\ref{explanationuncorrected}), except for $\langle\delta\bbh{F}\rangle=0$. This leads to (\ref{mockscalingcorrected}). If now we keep $\bb{C}$ fixed and we estimate only $\bbh{\Psi}$ from the simulations, we get
\begin{equation}
\label{tempcovarianceestimate}
\h{\Sigma}_\bb{p} = (\bbh{F}+\delta\bbh{F})^{-1}\bb{d}_0'^T(\bbh{\Psi}+\delta\bbh{\Psi})\bb{C}(\bbh{\Psi}+\delta\bbh{\Psi})\bb{d}_0'(\bbh{F}+\delta\bbh{F})^{-1}
\end{equation}
%
If we isolate the second order terms in (\ref{tempcovarianceestimate}), the result is 
\begin{equation}
\h{\Sigma}_\bb{p}\vert_2 = \bb{F}^{-1}(\bb{d}_0'^T\delta\bbh{\Psi}\bb{C}\delta\bbh{\Psi}\bb{d}_0'-\delta{\bbh{F}}\bb{F}^{-1}\delta{\bbh{F}})\bb{F}^{-1}
\end{equation} 
%
The expectation values of the quadratic fluctuations are easily computed using (\ref{psifluctuations}):
\begin{equation}
\begin{matrix}
& \langle\bb{d}_0'^T\delta\bbh{\Psi}\bb{C}\delta\bbh{\Psi}\bb{d}_0'\rangle = B(1+N_b)\bb{F} \\ \\
& \langle\delta{\bbh{F}}\bb{F}^{-1}\delta{\bbh{F}}\rangle = B(1+N_p)\bb{F}
\end{matrix}
\end{equation}
%
From which (\ref{dodelsonscaling}) immediately follows. 
\label{lastpage}
\end{document}

>>>>

\begin{figure*}
\includegraphics[scale=0.3]{Figures/effective_nb.eps}
\includegraphics[scale=0.3]{Figures/effective_nb_gaussian.eps}
\caption{Effective dimesionality of the feature space, $D$, as a function of the number of bands $N_b$, for the features outlined in Table \ref{featuretable}.}
\label{effectivenb}
\end{figure*}

@@

\begin{equation}
\h{\Sigma}_\bb{p} = \bb{F}^{-1} + \bb{F}^{-1}\left(- \delta{\bbh{F}}+ \delta{\bbh{F}}\bb{F}^{-1}\delta{\bbh{F}}\right)\bb{F}^{-1}  
\end{equation}  
%
If we use the precision estimator $\bbh{\Psi}=\bb{\Psi}+\delta\bbh{\Psi}$ and do not correct for the bias (\ref{psibias}), we have to use the facts that
\begin{equation}
\begin{matrix}
& \langle\delta\bbh{\Psi}\rangle = \frac{1+N_b}{N_r-N_b-2}\bb{\Psi} \\ \\
& \langle\delta\h{\Psi}_{ij}\delta\h{\Psi}_{kl}\rangle = \frac{A([(N_r-1)^2+(1+N_b)^2]\Psi_{ij}\Psi_{kl} + B(N_r-1)^2(\Psi_{ik}\Psi_{kl}+\Psi_{il}\Psi_{jk})}{(N_r-N_b-2)^2}
\end{matrix}
\end{equation}
%
Keeping only the leading order $O(1/N_r)$ in the expansion we get the results
\begin{equation}
\label{explanationuncorrected}
\begin{matrix}
& \langle\delta\bbh{F}\rangle = \left(\frac{1+N_b}{N_r}\right)\bb{F} \\ \\
& \langle\delta{\bbh{F}}\bb{F}^{-1}\delta{\bbh{F}}\rangle = B(1+N_p)\bb{F}
\end{matrix}
\end{equation}
%
which leads immediately to (\ref{mockscalinguncorrected}). Now suppose we correct for the bias in the precision estimator, and use the unbiased $\bbh{\Psi}$ for which $\delta\bbh{\Psi}=0$. This leads to equation (\ref{psifluctuations}) for the quadratic fluctuations in the precision matrix, and to the same (\ref{explanationuncorrected}), except for $\langle\delta\bbh{F}\rangle=0$. This leads to (\ref{mockscalingcorrected}). If now we keep $\bb{C}$ fixed and we estimate only $\bbh{\Psi}$ from the simulations, we get
\begin{equation}
\label{tempcovarianceestimate}
\h{\Sigma}_\bb{p} = (\bbh{F}+\delta\bbh{F})^{-1}\bb{d}_0'^T(\bbh{\Psi}+\delta\bbh{\Psi})\bb{C}(\bbh{\Psi}+\delta\bbh{\Psi})\bb{d}_0'(\bbh{F}+\delta\bbh{F})^{-1}
\end{equation}
%
If we isolate the second order terms in (\ref{tempcovarianceestimate}), the result is 
\begin{equation}
\h{\Sigma}_\bb{p}\vert_2 = \bb{F}^{-1}(\bb{d}_0'^T\delta\bbh{\Psi}\bb{C}\delta\bbh{\Psi}\bb{d}_0'-\delta{\bbh{F}}\bb{F}^{-1}\delta{\bbh{F}})\bb{F}^{-1}
\end{equation} 
%
The expectation values of the quadratic fluctuations are easily computed using (\ref{psifluctuations}):
\begin{equation}
\begin{matrix}
& \langle\bb{d}_0'^T\delta\bbh{\Psi}\bb{C}\delta\bbh{\Psi}\bb{d}_0'\rangle = B(1+N_b)\bb{F} \\ \\
& \langle\delta{\bbh{F}}\bb{F}^{-1}\delta{\bbh{F}}\rangle = B(1+N_p)\bb{F}
\end{matrix}
\end{equation}
%
From which (\ref{dodelsonscaling}) immediately follows. 
\label{lastpage}
\end{document}
